%
% $Id$
%
% Copyright (c)  2007  Tim Niemueller, AllemaniACs RoboCup Team.
%
% Created: Wed Jan 24 2007 15:28:35

\section{Retrospective}

\frame{\tableofcontents[currentsection,hideothersubsections]}

\subsection{RCSoft Drawbacks}
\begin{frame}
  \frametitle{Code Management Flaws}
  \begin{itemize}
  \item CVS hackery took place
  \item Many dependencies
  \item External libs inside the source tree
  \item Dependencies not documented and even somewhat hidden
  \item Inefficient build system with long build times and huge Makefiles
  \end{itemize}
  \begin{block}<2>{}
    All of these problems can be fixed inside RCSoft itself
    with some effort.
  \end{block}
\end{frame}


\begin{frame}
  \frametitle{Error Inducing Problems}
  \begin{itemize}
  \item Hard to debug with gdb (signal pollution)
  \item Code polluted (i.e. two approaches in BB)
  \item No detection of multiple module instances or BB writers
  \item Overhead due to process switches
  \item Insufficient config system (no long-time storage)
  \item Parameters unknown or even ``working against each other''
  \item No central logging, just logging transferred data that made it
    through the network
  \end{itemize}
  \begin{block}<2>{}
    Besides GDB problem this can be fixed inside RCSoft with
    a re-factoring, cleanup and fixing development cycle.
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{Performance Issues}
  \begin{itemize}
  \item Long time from power-on to working robot
  \item Global storage locking
  \item Polling everywhere, no events
  \item Overhead due to process switches
  \item All processes run continuously (even if no other process
    can make use of the result)
  \end{itemize}
  \begin{block}<2>{}
    Influenced by hardware performance. No easy way of fixing
    these problems inside RCSoft.
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{No Guarantees - no Timing}
  \begin{itemize}
  \item No timing guarantees, not even information
  \item No synchronization
  \item No information about data age
  \item No in-cycle-guarantee
  \end{itemize}
  \begin{block}<2>{}
    RCSoft probably wastes a lot of time calculating data
    twice before it is actually used. No information available
    about program flow. No way to fix this without major changes.
  \end{block}
\end{frame}

\subsection{RCSoft Benefits}
\begin{frame}
  \frametitle{RCSoft's Good Stuff}
  \begin{itemize}[<+->]
  \item Modular structure
  \item Unified information exchange (BlackBoard)
  \item Similarities in basic program structure
  \item Network transparency for information exchange
  \item Many tools, although many sub-optimal
  \end{itemize}
  \begin{block}<6>{}
    Start over from scratch. Keep the good ideas, improve or replace the
    not-so-good ones.
  \end{block}
\end{frame}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "fawkes-glance"
%%% End: 
